Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-25 paper/paper.Rmd
added overview paragraph to Intro

>>>>

The purpose of this paper is to give an overview of the methods implemented in the R package \pkg{mlr3spatiotempcv}.
After presenting the conceptual background in the following section, we will outline the overall structure of the \pkg{mlr3spatiotempcv} package.
We will then compare and contrast the various spatial and spatiotemporal partitioning techniques, before we demonstrate their application in a machine-learning model assessment in the following section.
We finally discuss implications and provide an outlook.
